dads manual

### 2020-11-09 inst/gitbook/02_make.traits.Rmd
Updated book

# Detailed functions

## Making trait processes with `make.traits()`

@@

### The process (`process`)

@@

### The number of traits `n` and the starting values `start`

@@

### Extra argument for the processes with `process.args`

@@

### Naming the traits with `trait.names`

@@

### Combining multiple traits with `add`

@@

### Testing the traits with `test`

@@

>>>>

# Making trait processes with `make.traits()`

@@

## The process (`process`)

@@

## The number of traits `n` and the starting values `start`

@@

## Extra argument for the processes with `process.args`

@@

## Naming the traits with `trait.names`

@@

## Combining multiple traits with `add`

@@

## Testing the traits with `test`

@@

## Templates for making your very own process

As detailed above, any process of your own design will work as long as it is a function that takes at least the arguments `x0` and `edge.length`.
You can be imaginative and creative when designing your own process but here are two detailed example functions for a unidimensional Brownian Motion and Ornstein-Uhlenbeck process that you can use for a start (or not).
Remember it is good practice for `dads` processes to set all the arguments but `x0` with default values (just in case).
Also, note that the functions below are not equal to the already implemented `BM.process` and `OU.process` but are rather generalised/simplified version that you can use as a template

### A simple Brownian Motion process template

```{r}
## A simple Brownian motion process
my.BM.process <- function(x0, edge.length = 1, sd = 1, ...) {
    ## Drawing a random number from a normal distribution
    ## with x0 as the and a given standard deviation
    ## and depending on branch (edge) length
    result <- rnorm(n = 1, mean = x0, sd = sd * edge.length)

    ## Return the number
    return(result)
}
```

### A simple Ornstein-Uhlenbeck process template

```{r}
## A simple Ornstein-Uhlenbeck motion process
function(x0, edge.length = 1, var = 1, alpha = 1, ...) {
    ## Calculate the mean based on alpha
    mean <- x0 * exp(-alpha)
    ## Calculate the standard deviation based on alpha and the variance
    sd <- sqrt(var/(2 * alpha) * (1 - exp(-2 * alpha)))
    ## Draw a random number from a normal distribution
    ## using this mean and standard deviation
    ## and depending on branch (edge) length
    result <- rnorm(n = 1, mean = mean, sd = sd * branch.length)

    ## Return the number
    return(result)
}
```

### 2020-11-09 inst/gitbook/index.Rmd
Updated book

>>>>

## How does `dads` work?

Basically, the `dads` function intakes your personalised `traits`, `modifiers` and `events` to generate your disparity and diversity.
You will find more details about how these objects (`traits`, `modifiers` and `events`) work in the rest of the tutorial but here is a graphical representation of how `dads` work:

![Schematised summary of the `dads` package architecture](dads_structure.pdf)
